---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GarminCSVr

<!-- badges: start -->
<!-- badges: end -->

A simple R package to process Garmin CSV files for running analysis.

## Installation

You can install the development version of GarminCSVr from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("quantixed/GarminCSVr")
```

## Example

Using CSVs downloaded from the Activities section of your Garmin Connect account, you can use GarminCSVr to analyze your running data.

Store the CSV files in a folder named `Data` in your working directory, then run the following code:

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(GarminCSVr)
## basic example code
summarise_my_running <- function(from, to, annual){
  # readAndCalc equivalent 
  process_data(activityStr = "running", fromStr = from, toStr = to, km = annual)
  
  # TSS score
  find_form(from = from, to = to)
  
  # distance map
  distanceTreemap(from = from, to = to)
  
  # calendar view
  calendarView(from = from, to = to)
}
summarise_my_running(from = "2023-01-01", to = "2023-12-31", annual = 1500)
```
