---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GarminCSVr

<!-- badges: start -->
<!-- badges: end -->

A simple R package to process Garmin CSV files for running analysis.

## Installation

You can install the development version of GarminCSVr from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("quantixed/GarminCSVr")
```

## Usage

Using CSVs downloaded from the Activities section of your Garmin Connect account, you can use GarminCSVr to analyze your running data (see note below for more information).

Store the CSV files in a folder named `Data` in your working directory, then run the following code to summarize your activities for the year 2023 with an annual target of 1500 km:

```{r example, eval=FALSE}
library(GarminCSVr)
## basic example code
summarise_activities(from = "2023-01-01", to = "2023-12-31", annual = 1500)
```

This will generate several plots including progress towards your target, Training Stress Score (TSS) form analysis, a distance treemap, and a calendar view of your activities. The plots will be saved in the `Output/Plots` directory.

The idea with `summarise_activities()` is to track up to one year's worth of data as you strive to reach an annual target.

If you have several years of data, you can use `compare_years()` different years of activities

```{r example1, eval=FALSE}
library(GarminCSVr)
## compare all years
compare_years()
## compare years with date range
compare_years(from = "2021-01-01", to = "2024-12-31")
```


## Go exploring

Instead of using the automated summaries, you can also use the individual functions to explore your data in more detail. See the function documentation for more details on how to use each function.

```{r example2, eval=FALSE}
library(ggplot2)
# load all running data
df <- load_garmin_data(minimal = FALSE)
# this will load all data, filtered for running, from the default Data directory
# into a data frame

# plot distribution of daily distances by year
df$Year <- format(df$Date, "%Y")
ggplot(df, aes(x = Year, y = Distance, fill = Year)) +
  geom_boxplot() +
  labs(title = "Yearly Distribution of Daily Distances",
       x = "Year",
       y = "Distance (km)") +
  theme_minimal() +
  theme(legend.position = "none")
```


## Example data

The idea is to analyse your own data, but in case you want to try out the package first, you can run this example:

```{r example3, eval=FALSE}
library(GarminCSVr)
# example data included in the package
# summarise activities for 2025 with a target of 1500 km
summarise_activities(datadir = system.file("extdata",package = "GarminCSVr"),
                     from = "2025-01-01", to = "2025-12-31", target = 1500)
# comparison of years using the example data
compare_years(datadir = system.file("extdata",package = "GarminCSVr"))
```

If you run this in a clean RStudio project, the example will create the `Output/Plots` directory in your working directory and save the plots there.

## Note

On Garmin Connect, you can download your activity data as CSV files from the Activities section. Select the activities you want to analyze, and use the "Export" option to download them in CSV format. Save these files in the `Data` directory for processing with GarminCSVr.

You can scroll down in Garmin Connect to go back in time and get as many activities as you need.

If you've exported all the activities, and then later export more activities, just add the new CSV files to the `Data` directory. GarminCSVr will process all CSV files in that directory each time you run the analysis and will handle duplicates automatically.

If you'd like to analyse Cycling or other activity types, you can specify the activity type in the function calls, e.g., `activity = "Cycling"`. It should work but has not been tested thoroughly.
