---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# GarminCSVr

<!-- badges: start -->
<!-- badges: end -->

A simple R package to process Garmin CSV files for running analysis.

## Installation

You can install the development version of GarminCSVr from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("quantixed/GarminCSVr")
```

## Example

Using CSVs downloaded from the Activities section of your Garmin Connect account, you can use GarminCSVr to analyze your running data.

Store the CSV files in a folder named `Data` in your working directory, then run the following code to summarize your activities for the year 2023 with an annual target of 1500 km:

```{r example, eval=FALSE}
library(GarminCSVr)
## basic example code
summarise_activities(from = "2023-01-01", to = "2023-12-31", annual = 1500)
```
